---
title: "run_analysis.Rmd"
date: '2017-06-19'
output: html_document
---

## Peer-graded Assignment: Getting and Cleaning Data 
```{r}
# 1. Downloading dataset
if(!file.exists("./data")){dir.create("./data")}
fileUrl <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
download.file(fileUrl,destfile="./data/Dataset.zip")

# Unzip dataSet to /data directory
unzip(zipfile="./data/Dataset.zip",exdir="./data")
```
# 2. Merge the training and the test sets to create one data set:

# 3. Reading trainings tables:
```{r}
x_train <- read.table("./data/UCI HAR Dataset/train/X_train.txt")
y_train <- read.table("./data/UCI HAR Dataset/train/y_train.txt")
subject_train <- read.table("./data/UCI HAR Dataset/train/subject_train.txt")
```
# 4. Reading testing tables:
```{r}
x_test <- read.table("./data/UCI HAR Dataset/test/X_test.txt")
y_test <- read.table("./data/UCI HAR Dataset/test/y_test.txt")
subject_test <- read.table("./data/UCI HAR Dataset/test/subject_test.txt")
```
# 5. Reading feature vector:
```{r}
features <- read.table('./data/UCI HAR Dataset/features.txt')
```
# 6. Reading activity labels:
```{r}
activityLabels = read.table('./data/UCI HAR Dataset/activity_labels.txt')
```
# 7. Assigning column names:
```{r}
colnames(x_train) <- features[,2] 
colnames(y_train) <-"activityId"
colnames(subject_train) <- "subjectId"
colnames(x_test) <- features[,2] 
colnames(y_test) <- "activityId"
colnames(subject_test) <- "subjectId"
colnames(activityLabels) <- c('activityId','activityType')
```
# 8. Merging all data in one set:
```{r}
mrg_train <- cbind(y_train, subject_train, x_train)
mrg_test <- cbind(y_test, subject_test, x_test)
setAllInOne <- rbind(mrg_train, mrg_test)
```
# 9. Extract only the measurements on the mean and standard deviation for each measurement.

# 10. Reading column names:
```{r}
colNames <- colnames(setAllInOne)
```
# 11. Create vector for defining ID, mean and standard deviation:
```{r}
mean_and_std <- (grepl("activityId" , colNames) | grepl("subjectId" , colNames) | 
grepl("mean.." , colNames) | grepl("std.." , colNames))
```
# 12. Making nessesary subset from setAllInOne:
```{r}
setForMeanAndStd <- setAllInOne[ , mean_and_std == TRUE]
```
# 13. Use descriptive activity names to name the activities in the data set:
```{r}
setWithActivityNames <- merge(setForMeanAndStd, activityLabels, by='activityId', all.x=TRUE)
```
# 14. Creating a second, independent tidy data set with the average of each variable for each activity and each subject:

# 15. Making second tidy data set 
```{r}
secTidySet <- aggregate(. ~subjectId + activityId, setWithActivityNames, mean)
secTidySet <- secTidySet[order(secTidySet$subjectId, secTidySet$activityId),]
```
# 16. Writing second independent tidy data set for each activity and each subject in txt file
```{r}
write.table(secTidySet, "secTidySet.txt", row.name=FALSE)
```